### 2023-11-07 main.tex
'

\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, arguing as in \eqref{remove-exponent}, the coefficient \eqref{ResulsBasis} when $N=2$ are written as
By varying $q$ and $\ell_{1},\ldots,\ell_{q}$, we have a one-to-one mapping with $\bm{\tau}$, therefore, we write 

@@

\textbf{Remark:}  We aim to find equation \eqref{ABS_1} in the case $N=2$. For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty. We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones. We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected. For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e. the coordinate where the particle with label $\ell_{i}$ is placed. We this notation we have that 

@@

	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{i=x_{\ell_{k}}}^{L}c_{i}\right)\dt

@@

Observing that
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\co
we finally obtain 
Therefore, considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP. 

@@

In this subsection we show that, if we stop distinguishing particles, we retrieve the non-equilibrium steady state correlations found in \cite{frassek2020eigenstates}. Moreover, for the sake of completeness, we also report the eigenvectors $|\Psi^{''}\rangle$ and $|\Psi^{'}\rangle$ when particles are indistinguishable.
\textbf{Proof:} Starting from \eqref{exactCorrelations_1} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$, such that $q\in\{0,\ldots,m\}$. There are many values of $c$'s that give the same $q$, therefore we define $q$ labels for the selected particles $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. For any $q$, we identify $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ coordinates where the $c_{x_{\ell_{i}}}=1$, then we have that 
Varying all possible $c$'s in \eqref{exactCorrelation_1} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain that 
\paragraph{$|\Psi^{''}\rangle$ for SSEP}
\paragraph{$|\Psi^{'}\rangle$ for SSEP}

>>>>

@@

\textbf{Remark:}  
The computations made for the multi-species stirring process can be specialized for the colour-blind case, i.e. the situation in which only one type of non-empty particle is considered. In this situation we retrieve the SSEP, already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations. 
	H=H_{left}+\sum_{x=1}^{L-1}H_{x,x+1}+H_{right}
	H_{x,x+1}=\sum_{a,b=1}^{2}\left(e_{ab}\otimes e_{ba}-e_{bb}\otimes e_{aa}\right)
		1-\alpha_{1}&\alpha_{1}\\
		\alpha_{2}&1-\alpha_{2}
	\end{pmatrix},\qquad H_{right}=\begin{pmatrix}
	1-\beta_{1}&\beta_{1}\\
	\beta_{2}&1-\beta_{2}
In this case, the similarity transformations read
	\mathcal{S}_{1}=\begin{pmatrix}
		1&0\\
		1&1
	\end{pmatrix},\qquad \mathcal{S}_{2}=\begin{pmatrix}
	1&-\beta_{1}\\
	0&1
Therefore, we have that $H^{'}$ has the following boundaries
	H^{'}_{left}=\begin{pmatrix}
		-1&\alpha_{1}\\
		0&0
	\end{pmatrix},\qquad H^{'}_{right}=\begin{pmatrix}
	-1&\beta_{1}\\
	0&0
and $H^{''}$ has the following boundaries 
	H^{''}_{left}=\begin{pmatrix}
		-1&(\alpha_{1}-\beta_{1})\\
		0&0
	\end{pmatrix},\qquad H^{''}_{right}=\begin{pmatrix}
	-1&0\\
	0&0
 We only report the main results, since the computations are just a specific case of the ones done in this section for the multi-species stirring process. 
\begin{equation}\label{correlations-SSEP}
\textbf{Proof:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$. There are many values of $c$'s that give the same $q$, therefore we define $q$ labels for the $c$'s equal to $1$ denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ and such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$, i.e. $c_{x_{\ell_{i}}}=1$ for $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$. Therefore, we have 
\begin{equation}\label{Gamma-product}
Varying all possible $c$'s in \eqref{exactCorrelations} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain that 
thus, \eqref{correlations-SSEP} follows. 
\paragraph{$|\Psi^{''}\rangle$ for SSEP} When we stop distinguishing colours we have that 
\begin{equation}\label{psiII-SSEP}
\textbf{Proof:} 
We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, arguing as in \eqref{remove-exponent} and using \eqref{Gamma-product} we have that 
By varying $q$ and $\ell_{1},\ldots,\ell_{q}$, we have a one-to-one mapping with $\bm{\tau}$, therefore we obtain \eqref{psiII-SSEP}.
\paragraph{$|\Psi^{'}\rangle$ for SSEP} In the colour-blind case, the ground state of $H^{'}$ reads
	|\Psi^{'}\rangle=\sum_{\bm{\tau}\in\Omega}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle
 \textbf{Proof:} For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty. We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones. We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected. For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e. the coordinate where the particle with label $\ell_{i}$ is placed. We this notation we have that 

@@

	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)\dt

@@

Therefore, using \eqref{Gamma-product} and by considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP.

@@
